Random forest cross-validation

### 2024-05-22 scripts/random_forest_cross_validation.qmd
modification to not use the country variable for the inference

```{r}
data_random_forest_calibration = data_random_forest %>% 
    filter (dataset == "Calibration subset") %>%
    select (- pmid, - e.rel, - dataset)
```

>>>>

```{r}
data_random_forest_calibration = data_random_forest %>% 
    filter (dataset == "Calibration subset") %>%
    select (- pmid, - e.rel, - dataset, - country)
```
